FAIR Theory: Applying Open Science Principles to the Construction and Iterative Improvement of Scientific Theories

### 2024-05-15 manuscript.Rmd
update 2024-05-15 16:18:17.547173

Based on this example: https://www.r-bloggers.com/2019/08/causal-inference-with-dags-in-r/

>>>>

This protocol shows how to use DAGs for causal inference, including the detection of a violation of the initial model and subsequent adaptation of the DAG. We could use that to illustrate updating FAIR theory:

https://currentprotocols.onlinelibrary.wiley.com/doi/full/10.1002/cpz1.45

We can find more examples of causal inference with DAGs in these tutorials:

https://www.r-bloggers.com/2019/08/causal-inference-with-dags-in-r/

https://www.r-bloggers.com/2018/08/applications-of-dags-in-causal-inference/
